---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# dfsummary

<!-- badges: start -->
[![R-CMD-check](https://github.com/thomas-rasmussen/dfsummary/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/thomas-rasmussen/dfsummary/actions/workflows/R-CMD-check.yaml)
[![test-coverage](https://github.com/thomas-rasmussen/dfsummary/actions/workflows/test-coverage.yaml/badge.svg)](https://github.com/thomas-rasmussen/dfsummary/actions/workflows/test-coverage.yaml)
<!-- badges: end -->

The goal of dfsummary is to make descriptive summries of datasets, where any person-sensitive information is automatically masked. In contrast to other packages, eg the excellent `gtsummary` package, this package does not aim to provide presentation-ready tables, but instead focuses on keeping things simple by relying only on the `data.table` package for efficient summarization. The summarized data is returned as a simple data.table and the user can then finalize the table themselves using eg the `gt` or `flextable` package.

## Installation

You can install the development version of dfsummary from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("thomas-rasmussen/dfsummary")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(dfsummary)
## basic example code
```

