---
title: "Introduction to dfsummary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dfsummary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dfsummary)
```

# Introduction

Creating descriptive summaries of variables in data.frames are a common task. In
the context of summarizing patient characteristics of a population, individual
level data is often person-sensitive and proper precautions have to be made to
be sure that the summarized data can not be used to identify data on individuals.
The main aim of **dfsummary** is to provide functions for summarizing data and
automatically mask any descriptive summary statistics that are deemed
person-sensitive. A secondary aim of **dfsummary** is to keep things simple:
the package depends only on **data.table**, which only depends on R itself. Also,
the output is a simple data.table. As a consequence, the focus is *not* to
make publication-ready tables; it is up to the user to finalize the tables. That
being said, the output is formatted to facilitate use of other packages like
**gt** and **flextable** to finalize the tables for publication, and we show
examples of how we imagine one could do so.

# Summarize a data.frame

To illustrate how the package can summarize a data.frame, we will use the infert
dataset from the **datasets** package.

```{r}

dt <- tbl_summary(
  infert,
  vars = c("age", "parity"),
  types = c(parity = "cat"),
  by = "case",
)
```

# Illustrate masking

Run same code, but now with masking. Explain what was masked and why.


# Finalize table for publication using **gt**

# Finalize table for publication using **flextable**

