---
title: "Introduction to dfsummary"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to dfsummary}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(dfsummary)
library(data.table)
```

# Introduction

Creating descriptive summaries of variables in data.frames are a common task. In
the context of summarizing patient characteristics of a population, individual
level data is often person-sensitive and proper precautions have to be made to
be sure that the summarized data can not be used to identify data on individuals.
The main aim of **dfsummary** is to provide functions for summarizing data and
automatically mask any descriptive summary statistics that are deemed
person-sensitive. A secondary aim of **dfsummary** is to keep things simple:
the package depends only on **data.table** (which only depends on R itself) and
the summarized data is returned in a data.frame.

# Summarize a data.frame

To illustrate how the package works, we will use a simple simulated dataset
imitating a population with information on an exposure variable, and different
types of patient characteristics.

```{r}
set.seed(1)
n <- 20
pop <-data.frame(
  exposure = sample(c("no", "yes"), n, replace = TRUE),
  cat_var = sample(c("A", "B", "C"), n, replace = TRUE),
  bin_var = sample(c(0, 1), n, replace = TRUE),
  cont_var = rnorm(n)
)

pop
```

Now lets summarize the data using the `tbl_summary` function from the package.

```{r}
summarized_pop <- tbl_summary(
  x = pop,
  vars = c("cat_var", "bin_var", "cont_var"),
  by = "exposure"
)

summarized_pop
```

By design, the summarized data is in long format. It is up to the user to make
the aggregated data look more presentable. Lets start by restructuring the data
to a wider format, with a column for each exposure level.

```{r}
wide_dat <- dcast(
  summarized_pop,
  .var_name + .var_level ~ .by,
  value.var = ".stat_value"
)

wide_dat
```



# Illustrate masking

We can see that the summarized data contains aggregated counts larger than zero
and smaller than five; values often considered person-sensitive. Person-sensitive
counts can be automatically masked using the `mask` argument.

```{r}
pop |>
  tbl_summary(
    vars = c("cat_var", "bin_var", "cont_var"),
    by = "exposure",
    mask = TRUE
  ) |>
  dcast(
    .var_name + .var_level ~ .by,
    value.var = ".stat_value"
  ) 
  
```
We can see that quite a lot has beene masked. Why? See "masking" vignette for more
information?


# Finalize table for publication using **gt**

# Finalize table for publication using **flextable**

